Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-19 report/report.tex
Add reference to Müller et al
Add figure illustrating point matching algorithm

This project has dealt with the feasibility of including footpath data when generating 3D representations of OSM data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.
The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities, since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity. (***find reference)

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship.
Footprints from different datasets may be formed at a different level of detail.
Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm \textbf{(Douglas and Peucker, 1973)}, to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
In either case The Oriented Minimum Bounding Rectangle (OMBR) is calculated for the two polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coinside with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.

>>>>

This project has dealt with the feasibility of including footpath data when generating 3D representations of OSM data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.

The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities, since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity. \textbf{(Müller et al, 2006)}

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship.
Footprints from different datasets may be formed at a different level of detail.
Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm \textbf{(Douglas and Peucker, 1973)}, to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
In either case The Oriented Minimum Bounding Rectangle (OMBR) is calculated for the two polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coinside with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.
See figure \ref{fig:vertex-match-algo} for an illustration of the algorithm that detects matching vertices between two similar polygons.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_vertex_match_algo}
    \caption{An illustration of the matching vertices detection algorithm. Starting from two highly similar polygons, the first step is to obtain both the Douglas-Peucker reduced polygons. The next step is to obtain the OMBRs of the reduced polygons, and for both polygons find the edges that coinside with the edges of the OMBRs. These edges are corresponding, and thus their end vertices form a matching vertex map between the original polygons.}
    \label{fig:vertex-match-algo}
\end{figure}
